Mergeable Types

### 2017-02-28 paper/meta.tex
Edits.

The proof is by the induction on the size of branching history. The
key observation is that the smallest history that is the union of
causal histories of two unmergeable versions (call them $v_i$ and
$v_j$) is smaller than the history that includes the unmergeable
versions. Since causal histories have maximum versions (respective
loci), which, by the inductive hypothesis, can be made mergeable, we
merge them to yield a new version $v$ that is the maximum of the
causal histories of both $v_i$ and $v_j$. If $v_i$ and $v_j$ are the
latest versions on their respective branches, the branches are now
mergeable.

>>>>

The proof is by the induction on the size of branching history. The
key observation is that the smallest history that is the union of
causal histories of two unmergeable versions (call them $v_i$ and
$v_j$) is smaller than the history that includes the unmergeable
versions. As shown in Fig.~\ref{fig:causal-history}, causal
histories have maximum versions (respective loci of $v_i$ and $v_j$),
which, by the inductive hypothesis, can be made mergeable. We
therefore can merge them to yield a new version $v$. Since $v$
immediately follows the loci of both $v_i$ and $v_j$, and since both
the versions are the latest versions on their respective branches, $v$
can be merged into $v_i$ and $v_j$ to create new versions $v_i'$ and
$v_j'$ on their respective branches, which have a single LCA - $v$.
Thus the branches are now mergeable.
